Tensor anisotropy as a tracer of cosmic voids

### 2015-02-16 cosmic_voids.tex
in the middle of writing conclusions

  \captionof{figure}{\small Volume size distribution of voids for both
  catalogues. FA-T-web (continuous red curves), FA-Vweb (dashed blue 
  curves). Left panel, total distributions. Right panel, distributions of 
  subcompensanted and overcompensanted voids. }

  \label{fig:volume_function}

@@

We propose in this paper a new method to find and describe void in
cosmological dark matter simulations.
The basis of our metho is the anisotropy of the eigenvalues from tensors
constructed to describe the cosmic web.

>>>>

  \captionof{figure}{\small Void size distribution (left) and fraction
    of overcompensated/subcompensated voids. The continous (dashed)
    curves correspond to the T-Web (V-Web).}
  \label{fig:volume_function}

@@

We propose in this paper that the anisotropy of the eigenvalues from
tensors constructed to describe the cosmic web is a good tracer of
cosmic voids. Based on this idea we go on to implement a watershed
algorithm o the fractional anisotropy to find voids voids in a N-body
cosmological simulations. We perform this tests on the results of two
different tensorial schemes, the T-Web and the V-web.

The first quantity we take a look at is the void size distribution
characterized by an effective radius. 
We find that for T-Web voids the shape of this function corresponds to
standard expectations. 
However, for the V-Web we find an overabundance of the smallest voids
due to artifacts in the web finding scheme in sheets and small
fragmented voids inside the largest voids already identified in the
T-Web, perhaps due to the complex velocity structure in large voids
compared to a simpler density/gravitational potential anatomy.

A second step in the characterization of the voids found by our method
was the separation into subcompensated and overcompensated samples. 
In the T-Web $60\%$ of the voids are overcompensated, meaning that
they are located in denser regions with a clear delimiting ridge. 
For the V-web the overcompensated fraction increases from $60\%$ to
$80\%$ as the void size decreases, supporting the picture of smaller
spurious voids located in matter sheets.

Finally we proceed with an ever more detailed void characterization
through the radially averaged profiles of density, radial velocity and
fractional anisotropy. 
In thi case we studied separately the subcompensated and
overcompensated voids, split this time in samples with different
effective radii.

In the density profiles the most interesting feature is that the 
profile has a similar shape for all the different void sizes once the
radial coordinate is expressed in units of the effective radius. 
In these profiles it is evident the presence of an overdense ridge
around $2<r/r_{\rm eff}<3$ for the overcompensated voids.
Subcompensated voids do not show such a ridge keeping its density
lower than the average value up to $r/r_{\rm eff}\sim 8$.

In other studies where voids are found using considerations on the
density fields the ridge is, almost by definition, located around
$r/r_{\rm eff}\sim 1$ and the subcompensated voids reach average
density around $r/r_{\rm eff}\sim 3$. 
This indicates that voids defined by boundaries in the FA are close to
a factor of $2$ smaller than voids found by density only considerations.

Our results extend the evidence for a universal density profile down
to smaller sizes as the one probed by \cite{Hamaus14}.
